\begin{thebibliography}{20}
\bibitem{ED22}Eugene Dorfman, 2022. \emph{How AI for Quality Control Enhances Yield in Manufacturing}.
\bibitem{BW22}Benjamin Wann, 2022. \emph{Why Do Manufacturers Struggle with Profitability?}.
\bibitem{DG20}David Greenfield, 2020. \emph{Why Do Manufacturers Struggle with Profitability?}.

\bibitem{LD13}Lenny Delligatti , 2013. \emph{SysML Distilled A Brief Guide}.

\bibitem{MA18} Mohamed FEZARI and Ali Al Dahoud, 2018. \emph{Integrated Development Environment “IDE” For Arduino}.
\bibitem{BMIPC17}Bernadette M. Randles, Milena S. Golshan, Irene V. Pasquetto and Christine L. Borgman, 2017. \emph{Using the Jupyter Notebook as a Tool for Open Science: An Empirical Study}.
\bibitem{SD20}Slobodan Dmitrović, 2020. \emph{ Modern C++ for Absolute Beginners: A Friendly Introduction to C++ Programming Language and C++11 to C++20 Standards}.
\bibitem{PS19}Prasanna Sattigeri, 2019. \emph{Deep Learning Inference: A Comprehensive Overview}.
\bibitem{AG19}Alex Gizis, 2019. \emph{5 Uses for Raspberry Pi Routers to Get Better Internet}.

\bibitem{CD21}Chakraborty D.,2021. \emph{ OpenCV Contour Approximation ( cv2.approxPolyDP ),}.
\bibitem{WG10}Willow Garage, 2010. \emph{OpenCV Reference Manual v2.2}.
\bibitem{HT}Handson Technology. \emph{ ESP32-CAM WiFi+Bluetooth+Camera Module Datasheet ),}.
\bibitem{E19}Espressif,2019. \emph{ ESP32-WROOM-32 Datasheet),}.
\bibitem{RSND}Raspberry Pi Software,(n.d.). \emph{Retrieved from the raspberrypi website}% https://www.raspberrypi.com/software/}
\bibitem{PYND}PuTTY. (n.d.). \emph{Retrieved from the PuTTY website} %https://www.putty.org/}
\bibitem{RVND}RealVNC. (n.d.). \emph{what is vnc remote access technology}% https://discover.realvnc.com/what-is-vnc-remote-access-technology}
\bibitem{GND}Geany. (n.d.). \emph{Retrieved from the geany website} %https://www.geany.org/}
\bibitem{GRND}Google Research . (n.d.). \emph{ Retrieved from Google Research website} %https://research.google.com/colaboratory/faq.html}
\bibitem{YC21}Pappu Kumar YadavJ. Alex ThomassonStephen W. SearcyRobert G. HardinUlisses Braga-NetoSorin C. PopescuDaniel E. MartinRoberto RodriguezKarem MezaJuan EncisoJorge Solórzano DiazTianyi Wang, 2021. \emph{ Assessing The Performance of YOLOv5 Algorithm For Detecting Volunteer Cotton Plants in Corn Fields at Three Different Growth Stages}.
\bibitem{KGMM21}Kathrin Blagec  , Georg Dorffner  , Milad Moradi , Matthias Samwald , 2020. \emph{ A critical analysis of metrics used for measuring progress in artificial intelligence }.
\bibitem{MG21}Marko Horvat, Gordan Gledec, 2022. \emph{A comparative study of YOLOv5 models performance for image localization and classification  }.
%\bibitem{MG21}Marko Horvat, Gordan Gledec, 2022. \emph{A comparative study of YOLOv5 models performance for image localization and classification  }.
\bibitem{U23}ultralytics, 2023. \emph{Retrieved from yolov5 github repository} % https://github.com/ultralytics/yolov5 }.
\bibitem{HW22}hitechwhizz, 2022. \emph{ Drawbacks and Benefits of Static IP Address}
\bibitem{RA19}Raspberry Pi Trading Ltd, 2019. \emph{ Raspberry Pi 4 Model B datasheet}
\bibitem{RA16}Raspberry Pi Trading Ltd, 2016. \emph{ Raspberry Pi 3 Model B+ datasheet}
\bibitem{T23}TESCA, 2023. \emph{Retrieved from TESCA webiste }
\bibitem{Tnd}Ifm efector,nd. \emph{ IFM O2D220  datasheet}
\bibitem{N22}Niklas Donges,2022. \emph{What Is Transfer Learning? Exploring the Popular Deep Learning Approach.}
\bibitem{And}Apollotechnical,nd. \emph{THE IMPORTANCE OF PRINTED CIRCUIT BOARDS FOR ELECTRONICS}


%https://www.hitechwhizz.com/2021/09/advantages-and-disadvantages-%drawbacks-benefits-of-static-ip-address.html.html.html}.
%https://pyimagesearch.com/2021/10/06/opencv-contour-approximation/



\end{thebibliography}
