%\documentclass{report}
%\input{includePackages.tex}
%\begin{document}
 \newpage

\begin{center}
\section*{Thanks}
\end{center}
  As I sit down to pen my farewell message at the end of my final year's internship, my mind is filled with a swirl of emotions. I can't help but feel a deep sense of gratitude towards the people who have helped me grow and develop over the past few months. Foremost among them is my supervisor, Mr Radhwen Aloui. His guidance, support, and mentorship have been invaluable to me, and I am truly grateful for the opportunity to have worked under his tutelage. His constant feedback and encouragement have helped me push my limits and reach new heights, particularly in the field of AI, where he encouraged me to excel and explore my potential.

I would also like to extend my thanks to my academic institution, where I have spent the past three years studying and learning. The institution's safe and educative environment has provided me with a solid foundation on which I can build my future. I will always cherish the memories of my time here, the friends I made, and the knowledge I gained.

Lastly, I would like to express my heartfelt gratitude to the jury members who took the time to review my rapport. I understand that your time is precious, and I appreciate your efforts in evaluating my work. I hope that my report reflects the hard work and dedication that I have put into my project over the past four months. Once again, thank you to everyone who has contributed to my growth and success during my internship, and I will always cherish the lessons and experiences that I have gained from this remarkable journey.
  \newpage
%\end{document}